\begin{rubric}{Selected Talks}

\entry*[2021] \textbf{Controlling the course of evolution in exogenously and endogenously changing environments}, York Cross-disciplinary Centre for Systems Analysis Seminar, York, United Kingdom (virtual). (Invited)

\entry*[2021] \textbf{Evolution of Ecological Communities: insights from Artificial Life}, Symposium on Astrobiology and Origins of Life: From Chemical Networks to Living Ecosystems, AAAS 2021 Annual Meeting (virtual).

\entry*[2020] \textbf{Introduction to controlling the speed and trajectory of evolution with counterdiabatic driving}, Artificial Life 2020, Montreal, Quebec, Canada (virtual).

\entry*[Postponed] \textbf{The role of ecology in producing life}, Breakthrough Discuss 2020. (Invited)

\entry*[2019] \textbf{Connections between open-ended evolution and chemical evolution}, Santa Fe Institute Working Group on Evolving Chemical Systems. (Invited)

\entry*[2019] \textbf{Evolutionary computation as a model system for studying eco-evolutionary dynamics}, Evolution 2019, Providence, Rhode Island, USA.

\entry*[2018] \textbf{Visualizing the Tape of Life: Exploring Evolutionary History with Virtual Reality}, Michigan State University Symposium on Virtual and Augmented Reality, East Lansing, Michigan, USA. (Invited)
%
\entry*[2018] \textbf{Exploring Genetic Programming Representations with MAP-Elites}, Genetic Programming in Theory and Practice, Ann Arbor, Michigan, USA.
%
\entry*[2017] \textbf{Applying Ecological Principles to Genetic Programming}, Genetic Programming in Theory and Practice, Ann Arbor, Michigan, USA.
%
\entry*[2016] \textbf{The Effects of Evolution and Spatial Structure on Diversity in Biological Reserves}, North American Congress for Conservation Biology, Madison, Wisconsin, USA. 
%
\entry*[2016] \textbf{Diversity in Biological and Computational Populations}, Synthesizing Concepts in Biology and Computer Science Workshop, Artificial Life XV, Cancun, Mexico. 
%
\entry*[2015] \textbf{Understanding Complexity Barriers in Evolving Systems}, Open-Ended Evolution Workshop, European Conference on Artificial Life, York, United Kingdom. 
%
% \entry*[2013] \textbf{Detecting Errors and Rare Events in Data Streams from Multiple Sensors}, Hubbard Brook Cooperator's Meeting, North Woodstock, New Hampshire, USA. 
%

\end{rubric}